%%%% Proceedings format for most of ACM conferences (with the exceptions listed below) and all ICPS volumes.
\documentclass[sigconf]{acmart}
%%%% As of March 2017, [siggraph] is no longer used. Please use sigconf (above) for SIGGRAPH conferences.

%%%% Proceedings format for SIGPLAN conferences 
% \documentclass[sigplan, anonymous, review]{acmart}

%%%% Proceedings format for SIGCHI conferences
% \documentclass[sigchi, review]{acmart}

%%%% To use the SIGCHI extended abstract template, please visit
% https://www.overleaf.com/read/zzzfqvkmrfzn


\usepackage{booktabs} % For formal tables
\usepackage{subfigure}
\usepackage{algorithmic}
\usepackage{amsthm}
% \usepackage{algorithm}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage{amsmath}
\usepackage{float}

% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}


% DOI
% \acmDOI{10.475/123_4}

% ISBN
% \acmISBN{123-4567-24-567/08/06}

%Conference
\acmConference[FAT*ML19]{FAT* ML conference}{January 2019}{Atlanta, Georgia USA}
\acmYear{2019}
\copyrightyear{2018}


%\acmArticle{4}
%\acmPrice{15.00}

% These commands are optional
%\acmBooktitle{Transactions of the ACM Woodstock conference}
\editor{}
\editor{}
\editor{}


\begin{document}
\title{Pareto-Efficient Subgroup Fairness via the lens of Causality and Confounding Factors}
%\titlenote{Produces the permission block, and
%  copyright information}
% \subtitle{Extended Abstract}
%\subtitlenote{The full version of the author's guide is available as
%  \texttt{acmart.pdf} document}


% \author{Ananth Balashankar}
%\authornote{}
%\orcid{1234-5678-9012}
%\affiliation{%
%  \institution{New York University}
%  \streetaddress{}
%  \city{New York}
%  \state{NY}
%  \postcode{10003}
%}
%\email{ananth@nyu.edu}

%\author{Alyssa Lees}
%\authornote{}
%\affiliation{%
%  \institution{Google RMI NYC}
%  \streetaddress{}
%  \city{New York}
%  \state{NY}
%  \postcode{10012}
%}
%\email{AlyssaLees@google.com}


% The default list of authors is too long for headers.
% \renewcommand{\shortauthors}{A. Balashankar et al.}


\begin{abstract}
Recent literature aimed at resolving concerns of inequity in machine learning models is often predicated on defining constraints with respect to specific predefined sensitive variables.  A sensitive variable is a feature, such as race or gender in a dataset containing user info, that should not exhibit conditionally discriminative behavior in output classification. Ensuring subgroup fairness based on the intersectionality of multiple sensitive variables in a dataset is critical for bias mitigation algorithms. Scaling existing bias minimizing techniques, such as equalizing odds, to ensure subgroup fairness may lead to scenarios where hard equality constraints are impossible to achieve. Similarly, relaxation of these constraints may lead to degradation in performance. Explicitly we explore edge-case scenarios where regularization of these sensitive variables via Lagrangian relaxation can exacerbate classification inequity within subgroups.  \par
In order to mitigate, we propose a softer constraint based on Pareto-efficiency which leads to better subgroup performance.  We also jointly explore how detection of potential causal confounding variables can drastically change the interpretation of fairness after adjusting for sensitive variable bias.  In such situations, interventions by domain experts may be necessary to interpret the confounding variables and to offer a holistic understanding of the tradeoffs in subgroup fairness.  We propose a methodology to identify and incorporate possible confounding variables into sensitive variable analysis to aid in this pursuit.  Evaluation on synthetic data and the UCI Adult dataset highlights the utility and increased performance with our approach.

\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below.
%


\maketitle

% \input{samplebody-conf}
\input{introduction}
\input{related}
\input{methodology}
\input{evaluation}
\input{conclusion}

% Bibliography 
\bibliographystyle{ACM-Reference-Format}
\bibliography{sample-bibliography}

\end{document}
